Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
small changes

Multi-collector are multiple independent garbage collectors thread / process that works independently on the heap to identify garbage. These collectors utilize multiple processors when there is a lot of compute resources being underutilized. In shared memory systems, when multiple processors are underutilized, this property helps to utilize processor cycles better. Apart from the processor utilization, the throughput of garbage collectors can be increased by multi-collector garbage collectors. These multi-collector garbage collector threads / processes communicate among themselves through memory in shared memory systems and through messages in distributed memory systems.

@@

Multi-collector garbage collectors are common among distributed memory systems. 
When multi-collector garbage collectors are used, conventional solutions require global barrier among all the collectors to communicate and share the information to identify garbage objects and delete them. With no global synchronization, the throughput of garbage collectors will be high and garbage collector algorithm scales well with this property.

>>>>

Multi-collector garbage collectors are collectors that have multiple independent garbage collector threads / processes that work independently on the heap to identify garbage. These collectors utilize multiple processors when compute resources are being underutilized. In shared memory systems, when multiple processors are underutilized, this property helps to utilize processor cycles better. Apart from the processor utilization, the throughput of garbage collectors can be increased by multi-collector garbage collectors. These multi-collector garbage collector threads / processes communicate among themselves through memory in shared memory systems and through messages in distributed memory systems.

@@

Multi-collector garbage collectors are common in distributed memory systems. 
When multi-collector garbage collectors are used, conventional solutions require a global barrier among all the collectors to communicate and share the information to identify garbage objects. With no global synchronization, the throughput of garbage collectors will be high and garbage collector algorithm scales well with this property.
